---
  title: "5-choice read in training"
output:
  html_document:
  df_print: paged
html_notebook:
  fig_height: 8
---

Reading in training
  
CURRENT AS OF:

*June 29th, 2022*

*UPDATE CURRENT DAY / OLD DAY IF YOU WANT TO ADD JUST ONE DAY OF NEW DATA, OR READ IN ALL TRAINING RUNS FROM HOME FOLDER*

This chunk will read in the libraries and functions we need

```{r, include=FALSE}

library(readr)
library(dplyr)
library(stringr)
library(magrittr)
library(tidyr)
library(ggplot2)
library(purrr)

read_plus = function(x) {
  read_csv(x,
           col_types = list(col_double(),
                            col_character(),
                            col_character())
           ) %>% 
    mutate(filename = x)
}

read_plus_skip1 = function(x) {
  read_csv(x, skip = 1) %>% 
    mutate(filename = x)
}

get_RT = function(x) {
  ifelse(str_detect(x,"latency"),
         as.numeric(paste(str_extract(x, "[^latency: ]+$"), sep = ""))/1000,
         NA)
}

st.err = function(x) {
  sd(x)/sqrt(length(x))
}

get_CV = function(x) {
  sd(x) / mean(x)
}
```


This chunk lists all the files in the folder we designate, and combines them into a single dataframe

```{r read in files}
listruns =
  
  list.files(path="FILEPATH TO NEW DATA, CURRENT DAY OR ALL DATA",
                                recursive = T,
             
                                 pattern = "*.csv",
             
                              full.names = T) %>%
  
  map_df(~ read_plus(.))
```

If we need to combine columns, this lets us do that

designate columns k1, k2, or k3 as needed

coalesce() combines them, replacing NAs with real values

```{r , message=FALSE, results=FALSE, include=FALSE}

selectdata_df = listruns %>%
  
  select(-"0") %>%
  
  rename(Time_ms = "experiment name:",
         k1 = kyle,
         k2 = Kyle,
         k3 = X3
         ) %>%
  
  mutate(Kyle = coalesce(k1, k2, k3)) %>%
  
  select(-k1, -k2, -k3,
         
         filename, Time_ms, Kyle)

```


Now, we will pull out what stage of training the animals are in, and their unique ID

```{r , message=FALSE, results=FALSE, include=FALSE}

datastage_set = selectdata_df %>% 
  
  group_by(filename) %>%
  
  mutate(
  
    Task = substr(Kyle[c(1)], 1, 11),
    
    Stage = case_when(
      
      str_detect(Task, "habituation") ~ -1,
      str_detect(Task, "Stage_0") ~ 0,
      str_detect(Task, "Stage_1") ~ 1,
      str_detect(Task, "Stage_2") ~ 2,
      str_detect(Task, "Stage_3") ~ 3,
      str_detect(Task, "Stage_4") ~ 4,
      str_detect(Task, "Stage_5") ~ 5,
      str_detect(Task, "Stage_6") ~ 6
      
    ),
    
    Date = substr(Kyle[c(4)], 1, 10),
    
    Box = substr(Kyle[c(1)], 1, 1),
    
    ID = Kyle[c(2)])

```


Now we will convert time to minutes from ms, and get rid of "NA" rows too.

```{r , message=FALSE, results=FALSE, include=FALSE}
datastage_new = datastage_set %>% 
  
  transmute( 
    
    Task = Task,
    
    Stage = Stage,
    
    Date = Date,
    
    Box = Box,
    
    ID = ID,
    
    Timestamp = as.numeric(paste(Time_ms))/60000,
    
    Kyle = Kyle
  
    ) %>% ungroup() 

datastage_new = na.omit(datastage_new)

```

```{r}

# datastage_old = read_csv("FILEPATH TO OLD DATA, IF ADDING NEW DATA TO OLD")

datastage = rbind(
  # datastage_old,
  datastage_new
)

write_csv(datastage, "FILEPATH AND NAME FOR RAW .CSV OUTPUT, OF ALL NEW DATA + OLD IF COMBINING")

```

For reward only phase: get correct, RT, RL for all

```{r}

Stage0_only = datastage %>%
  
  group_by(filename) %>%
  
  filter(Stage == 0) %>%
  
  filter(
    str_detect(Kyle, "taste_task")|
    str_detect(Kyle, "^poke_[1-6]$")|
    str_detect(Kyle, "Perseveration")|
    str_detect(Kyle, "Correct_response")|
    str_detect(Kyle, "Reward_taken")
         ) %>%
  
  mutate(Target = 6)

Stage0_correct = Stage0_only %>%
  filter(
    str_detect(Kyle, "taste_task")|
    str_detect(Kyle, "^poke_[1-5]$")|
    str_detect(Kyle, "Correct_response")|
    str_detect(Kyle, "Reward_taken")
  ) %>%
  mutate(
    Response = case_when(
      Kyle == "Correct_response" ~ "Correct"),
    Poke = case_when(
      Response == "Correct" ~ substr(dplyr::lag(Kyle, n=1, default = NA), 6, 6))
    )

Stage0_correct_RT = Stage0_correct %>%
  filter(Response == "Correct"|
           Kyle == "taste_task") %>%
  group_by(filename) %>%
  arrange(filename, Timestamp) %>%
  mutate(RT = Timestamp - dplyr::lag(Timestamp, n=1, default = NA)) %>%
  filter(Response == "Correct")


Stage0_correct_RL = Stage0_correct %>%
  filter(Response == "Correct"|
           str_detect(Kyle, "Reward_taken")) %>%
  group_by(filename) %>%
  arrange(filename, Timestamp) %>%
  mutate(Response = case_when(
            Kyle == "Reward_taken" ~ "Reward"
              ),
         RT = Timestamp - dplyr::lag(Timestamp, n=1, default = NA)) %>%
  filter(Response == "Reward")


Stage0_correct_RT_RL = rbind(
  Stage0_correct_RT,
  Stage0_correct_RL
) %>%
  group_by(filename) %>%
  arrange(filename, Timestamp) %>%
  mutate(RL = dplyr::lead(RT, n=1, default = NA),
         Port = Poke,
         Target = 6) %>%
  filter(Response == "Correct") %>%
  select(-Poke, -Kyle) %>%
  ungroup()


```


```{r }
# Pre staging rip -------------------------------------------------------------

Master_df_response = datastage %>% 
  
  filter(Stage > 0) %>% 
  
  group_by(filename) %>% 
  
  filter(str_detect(Kyle, "^poke_[1-6]$")|
           
           str_detect(Kyle, "Light")|
           str_detect(Kyle, "Correct_latency")|
           str_detect(Kyle, "Reward_latency")|
           
           str_detect(Kyle, "Incorrect_response")|
           str_detect(Kyle, "Incorrect_latency")|
           str_detect(Kyle, "Omission")|
           
           str_detect(Kyle, "ITI$")|
           str_detect(Kyle, "Premature_response")|
           str_detect(Kyle, "Premature_latency")|
           str_detect(Kyle, "Perseveration")|
           str_detect(Kyle, "Timeout_poke")
  )
```


```{r }
Master_df_quickrip = Master_df_response %>% 
  
  filter(Kyle != "Incorrect_response") %>% 
  
  mutate(
    
    Poke = ifelse(str_detect(Kyle, "^poke_[1-6]$"),
                  substr(Kyle, 6, 6),
                  NA),
    
    Light = ifelse(str_detect(Kyle, "^Light[1-5]$"),
                   substr(Kyle, 6, 6),
                   NA),
    
    Latency = get_RT(Kyle)
  )

```

```{r , message=FALSE, include= FALSE}

Master_df_target = Master_df_quickrip %>% 
  
  filter(str_detect(Kyle, "poke_[1-5]")|
           !is.na(Light)|
           str_detect(Kyle, "Omission|Incorrect|Reward")) %>% 
  
  group_by(filename) %>% 
  
  arrange(filename, Timestamp) %>% 
  
  mutate(
    
    Response = case_when(
      
      Light == dplyr::lead(Poke, n=1, default = NA) ~ "Correct",
      
      Light != dplyr::lead(Poke, n=1, default = NA) ~ "Incorrect",
      
      dplyr::lead(Kyle, n=1, default = NA) == "Omission" ~ "Omission"
    
      ),
    
    RT = case_when(
      
      Response == "Correct" ~ dplyr::lead(Timestamp, n=1, default = NA) - Timestamp,
      
      Response == "Incorrect" ~ dplyr::lead(Timestamp, n=1, default = NA) - Timestamp,
      
      Response == "Omission" ~ 0
      
      ),
    
    Target = Light,
    
    Port = case_when(
      
      Response == "Correct"|
        Response == "Incorrect" ~ as.numeric(dplyr::lead(Poke, n=1, default = NA)),
      
      Response == "Omission" ~ 0
      )
    ) %>%
  
  filter(Response == "Correct"|
           Response == "Incorrect"|
           Response == "Omission") %>% 
  
  select(-Kyle, -Poke, -Light, -Latency) %>%
  
  ungroup()

```

```{r , message=FALSE, include= FALSE}

Master_df_RL = Master_df_quickrip %>% 
  
  filter(!is.na(Light)|
           str_detect(Kyle, "Reward")) %>% 
  
  group_by(filename) %>% 
  
  arrange(filename, Timestamp) %>% 
  
  mutate(
    
    Reward = dplyr::lead(Kyle, n=1),
    
    Response = substr(Reward, 1, 6),
    
    RT = get_RT(Reward),
    
    Target = Light,
    
    Port = 6
    
    ) %>% 
  
  filter(!is.na(Target),
         str_detect(Response, "Reward")) %>% 
  
  select(-Kyle, -Poke, -Light, -Latency,
         -Reward) %>%
  
  ungroup()

```

```{r , message=FALSE, include= FALSE}

Master_df_Correct_RL = rbind(
  
  Master_df_target,
  Master_df_RL
  
  ) %>%
  
  group_by(filename) %>%
  
  arrange(filename, Timestamp) %>%
  
  mutate(RL = case_when(
    
    dplyr::lead(Response, n=1) == "Reward" ~ dplyr::lead(RT),
    
    dplyr::lead(Response, n=1) != "Reward" ~ 0
    
    )
    ) %>%
  
  filter(Response != "Reward") %>%
  
  ungroup()

```

```{r , message=FALSE, include= FALSE}

Master_df_persev = Master_df_quickrip %>% 
  
  filter(str_detect(Kyle, "poke_[1-5]")|
           str_detect(Kyle, "Perseveration")) %>% 
  
  
  group_by(filename) %>% 
  
  arrange(filename, Timestamp) %>% 
  
  mutate(
    
    Response = case_when(
      
      Kyle == "Perseveration" ~ "Perseverative"
      
      ),
    
    RT = 0,
    
    Target = 0,
    
    Port = case_when(
      
      Response == "Perseverative" ~ as.numeric(dplyr::lag(Poke, n=1, default = NA))
      
      ),
    
    RL = 0
    ) %>%
  
  filter(Response == "Perseverative") %>% 
  
  select(-Kyle, -Poke, -Light, -Latency) %>%
  
  ungroup()

```


```{r , message=FALSE, include= FALSE}

Master_df_timeout = Master_df_quickrip %>%
  
  filter(str_detect(Kyle, "poke_[1-5]")|
           str_detect(Kyle, "Timeout")) %>%
  
  group_by(filename) %>% 
  
  arrange(filename, Timestamp) %>%
  
  mutate(
    
    Response = case_when(
      
      Kyle == "Timeout_poke" ~ "Timeout"
      
      ),
    
    RT = 0,
    
    Target = 0,
    
    Port = case_when(
      
      Response == "Timeout" ~ as.numeric(dplyr::lag(Poke, n=1, default = NA))
      
      ),
    
    RL = 0
    ) %>%
  
  filter(Response == "Timeout") %>%
  
  select(-Kyle, -Poke, -Light, -Latency) %>%
  
  ungroup() 

```


```{r , message=FALSE, include= FALSE}

datastageset = Master_df_quickrip %>% 
  
  filter(str_detect(Kyle, "ITI")|
           str_detect(Kyle, "poke_[1-5]")|
           str_detect(Kyle, "Premature_response")) %>% 
  
  group_by(filename) %>% 
  
  arrange(filename, Timestamp) %>% 
  
  mutate(
    
    Response = case_when(
      
      Kyle == "ITI" & dplyr::lead(Kyle, n=2) == "Premature_response" ~ "Premature"
    
      ),
    
    RT = case_when(
      
      Response == "Premature" ~ dplyr::lead(Timestamp, n=2) - Timestamp,
    
      ),
    
    Target = 0,
    
    Port = case_when(
      
      Response == "Premature" ~ as.numeric(dplyr::lead(Poke, n=1, default = NA))
    
      ),
    
    RL = 0
  
    ) %>% 
  
  filter(Response == "Premature") %>% 
  
  select(-Kyle, -Poke, -Light, -Latency) %>% 
  
  ungroup()

```


```{r , message=FALSE}

Master_df_flex = rbind(
  
  Stage0_correct_RT_RL, # adding in for Reward phase correct pokes
  
  Master_df_Correct_RL,
  
  Master_df_persev,
  
  Master_df_timeout,
  
  datastageset
  
    ) %>% 
  
  arrange(filename, Timestamp) %>%
  
  group_by(ID) %>% 
  
  mutate(Session_all = match(Date, unique(Date))) %>%
  
  ungroup() %>% 

  group_by(Stage, ID) %>% 
    
  mutate(Session = match(Date, unique(Date))) %>%
    
  ungroup() %>%
  
  group_by(Stage, ID, Date) %>%
  
  mutate(
    
    Trial_case = case_when(
      
      Target > 0 ~ 1,
      
      Target == 0 ~ 0
      
    ),
    
    Trials = cumsum(Trial_case)
    
  ) %>% 
  
  ungroup() %>% 
  
  select(Task, Stage, Date, Session_all, Session, ID,
         
         Timestamp, Response, Trials,
         
         Port, Target, RT, RL, filename,
         
         -Box, -Trial_case)

write_csv(Master_df_flex,
          
        "FILEPATH AND NAME OF .CSV FOR PROCESSED DATA, AFTER PROCESSING THE RAW.CSV FILE")

```
