---
title: "5-choice training progress"
output: html_notebook
---

read in libraries and functions

# read in libraries and functions

```{r}

library(readr)
library(dplyr)
library(stringr)
library(magrittr)
library(tidyr)
library(ggplot2)
library(purrr)

library(ggrepel)

index <- function(x){
  as.integer(row.names(x))
}

```

read in data .csv, and add "demographic" info for each unique animal ID

# read in data, and MIA descriptions

```{r}
train = read_csv("PROCESSED DATA FILEPATH GOES HERE") %>% 
  
  mutate(
    
    Litter = case_when(),
    
    Sex = case_when(),
    
    Group = case_when()
    
  ) 

```

```{r}

train$ID <- factor(train$ID, levels = c())

```

# overall training progress by sex

```{r, fig.width=15, fig.height=8}

ggplot(train %>% 
         
         group_by(Group, Sex, Stage, ID, Session_all) %>% 
         
         summarise(n = n()),

       aes(Session_all,
           
           as.integer(Stage),
           
           fill = Group
           
           )) +
  
  facet_wrap(~ Sex) +

  geom_jitter(aes(color = Group),
              height = 0.1,
              width = 0.1) +

  stat_summary(aes(fill = Group),
               fun = "mean", geom = "line",
               size = 1) +

  stat_summary(fun.data = "mean_se", geom = "ribbon",
               alpha = 0.25) +
  
  scale_y_continuous(breaks = seq(0, 6, by = 1)) +
  
  # scale_color_manual(values = c("dodgerblue", "orange", "green2"))+
  #scale_fill_manual(values = c("dodgerblue", "orange", "green"))+

  ggtitle("Progress across training stages") +
  ylab("Stage of Training") +
  xlab("Day of Training") +

  theme_classic(base_size=22) +
  
  theme(axis.text = element_text(size = 14),
        strip.text.x = element_text(size = 16),
        title = element_text(size = 16)
        )

```

# overall training progress

```{r, fig.width=15, fig.height=8}

ggplot(train %>% 
         
         group_by(Group, Sex, Stage, ID, Session_all) %>% 
         
         summarise(n = n()),

       aes(Session_all,
           
           as.integer(Stage),
           
           fill = Group
           
           )) +
  
  # facet_wrap(~ Sex) +

  geom_jitter(aes(color = Group),
              height = 0.1,
              width = 0.1) +

  stat_summary(aes(fill = Group),
               fun = "mean", geom = "line",
               size = 1) +

  stat_summary(fun.data = "mean_se", geom = "ribbon",
               alpha = 0.25) +
  
  scale_y_continuous(breaks = seq(0, 6, by = 1)) +
  
  # scale_color_manual(values = c("dodgerblue", "orange", "green2"))+
  #scale_fill_manual(values = c("dodgerblue", "orange", "green"))+

  ggtitle("Progress across training stages") +
  ylab("Stage of Training") +
  xlab("Day of Training") +

  theme_classic(base_size=22) +
  
  theme(axis.text = element_text(size = 14),
        strip.text.x = element_text(size = 16),
        title = element_text(size = 16)
        )

```


# Stage 0 pass

```{r}

stage0 = train %>%
  
  filter(Stage == 0) %>%
  
  group_by(ID)

head(stage0)

```

How many sessions to graduate? 

```{r}

stage0 %>% 
  
  count(Group, Sex)

```


```{r}

pass0 = stage0 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
  ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n(),
         
         pass = case_when(
           
           Correct >= 45 ~ 3,
           
           Correct > 30 & lag(Correct, n = 1) < 30 ~ 1,
           
           Correct > 30 & lag(Correct, n = 1) > 30 ~ 2,
           
           TRUE ~ 0
           
         )) %>% 
    
    ungroup()

```


```{r, fig.width=18, fig.height=10}

ggplot(pass0,
  
  aes(Session,
      
      Correct,
      
      fill = as.factor(pass))) +
  
  facet_wrap( ~ ID, ncol = 12) +
  
  geom_hline(yintercept = 45,
             
             color = "red",
             
             alpha = 0.5) +
  
  geom_hline(yintercept = 30,
             
             color = "black",
             
             alpha = 0.5) +
    
  geom_col(alpha = 0.5) +
  
  # scale_fill_manual(values = c("black", "orange", "blue", "red")) +
    
  theme_classic(base_size=22)

```

```{r}

pass0sum = pass0 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass0sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

# Stage 1 to pass

```{r}

stage1 = train %>%
  
  filter(Stage == 1) %>%
  
  group_by(ID)

head(stage1)

```

How many sessions to graduate? 

```{r}

stage1 %>% 
  
  count(Group, Sex)

```
```{r}

pass1 = stage1 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
    ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n()) %>% 
    
    ungroup()

```

```{r}

promotion1 = stage1 %>%
  
  group_by(Group, Sex, ID, Session) %>%
  
  summarise(.nCor = sum(Response == "Correct") / 100 ,
            
            Corr = sum(Response == "Correct") / max(Trials),
            Accu = sum(Response == "Correct") /
                     (sum(Response == "Correct") + sum(Response == "Incorrect")),
            Omis = sum(Response == "Omission") / max(Trials),
            Prem = sum(Response == "Premature") / max(Trials),
            Pers = sum(Response == "Perseverative") / max(Trials),
            Time = sum(Response == "Timeout") / max(Trials)
            
            ) %>%
  
  pivot_longer(cols = .nCor:Time) %>% 
  
  ungroup()

```


```{r, fig.width=18, fig.height=10}

ggplot(promotion1 %>% 
         
         filter(name == "Corr"|
                  name == ".nCor"),

       aes(as.factor(Session),
           value,
           fill = name)

       ) +

  facet_wrap(~ ID,
             ncol = 10) +

  geom_hline(yintercept = 0.3,
             color = "darkgreen") +
  
  geom_hline(yintercept = 0.4,
             color = "dodgerblue") +
  
  stat_summary(fun = "mean", geom = "col",
               alpha = 0.5,
               position = position_dodge(width = 0.5), width = 0.5) +

  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.2, size = 0.5) +
  
  scale_fill_manual(values = c("darkgreen", "dodgerblue")) +

  ggtitle("%, # Correct during stage 1") +
  ylab("Correct #") +
  xlab("Session #") +

  theme_classic(base_size = 22)

```

```{r}

pass1sum = pass1 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass1sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

# Stage 2 to pass

```{r}

stage2 = train %>%
  
  filter(Stage == 2) %>%
  
  group_by(ID)

head(stage2)

```

How many sessions to graduate? 

```{r}

stage2 %>% 
  
  count(Group, Sex)

```
```{r}

promotion2 = train %>%
  
  filter(Stage == 2) %>%
  
  group_by(ID) %>% 
  
  mutate(Session = match(Date,
                         unique(Date))) %>% 
  
  ungroup() %>% 
  
  group_by(ID, Session) %>%
  
  summarise(.nCor = sum(Response == "Correct") / 100 ,
            
            Corr = sum(Response == "Correct") / max(Trials),
            Accu = sum(Response == "Correct") /
                     (sum(Response == "Correct") + sum(Response == "Incorrect")),
            Omis = sum(Response == "Omission") / max(Trials),
            Prem = sum(Response == "Premature") / max(Trials),
            Pers = sum(Response == "Perseverative") / max(Trials),
            Time = sum(Response == "Timeout") / max(Trials)
            
            ) %>%
  
  pivot_longer(cols = .nCor:Time) %>% 
  
  ungroup()

```


```{r, fig.width=12, fig.height=12}

ggplot(promotion2 %>% 
         
         filter(name == "Corr"|
                  name == ".nCor"),

       aes(as.factor(Session),
           value,
           fill = name)

       ) +

  facet_wrap(~ ID,
             ncol = 8) +

  geom_hline(yintercept = 0.4,
             color = "darkgreen") +
  
  geom_hline(yintercept = 0.5,
             color = "dodgerblue") +
  
  stat_summary(fun = "mean", geom = "col",
               alpha = 0.5,
               position = position_dodge(width = 0.5), width = 0.5) +

  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.2, size = 0.5) +
  
  scale_fill_manual(values = c("darkgreen", "dodgerblue")) +

  ggtitle("%, # Correct during stage 2") +
  ylab("Correct #") +
  xlab("Session #") +

  theme_classic(base_size = 22)

```

```{r}

pass2 = stage2 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
    ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n()) %>% 
    
    ungroup()

```


```{r}

pass2sum = pass2 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass2sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

# Stage 3 to pass

```{r}

stage3 = train %>%
  
  filter(Stage == 3) %>%
  
  group_by(ID)

head(stage3)

```

How many sessions to graduate? 

```{r}

stage3 %>% 
  
  count(Group, Sex)

```

```{r}

promotion3 = train %>%
  
  filter(Stage == 3) %>%
  
  group_by(ID) %>% 
  
  mutate(Session = match(Date,
                         unique(Date))) %>% 
  
  ungroup() %>% 
  
  group_by(ID, Session) %>%
  
  summarise(.nCor = sum(Response == "Correct") / 100 ,
            
            Corr = sum(Response == "Correct") / max(Trials),
            Accu = sum(Response == "Correct") /
                     (sum(Response == "Correct") + sum(Response == "Incorrect")),
            Omis = sum(Response == "Omission") / max(Trials),
            Prem = sum(Response == "Premature") / max(Trials),
            Pers = sum(Response == "Perseverative") / max(Trials),
            Time = sum(Response == "Timeout") / max(Trials)
            
            ) %>%
  
  pivot_longer(cols = .nCor:Time) %>% 
  
  ungroup()

```


```{r, fig.width=12, fig.height=12}

ggplot(promotion3 %>% 
         
         filter(name == "Accu"|
                  name == "Omis"),

       aes(as.factor(Session),
           value,
           fill = name)

       ) +

  facet_wrap(~ ID,
             ncol = 8) +

  geom_hline(yintercept = 0.8,
             color = "dodgerblue") +
  
  geom_hline(yintercept = 0.5,
             color = "red") +
  
  stat_summary(fun = "mean", geom = "col",
               alpha = 0.5,
               position = position_dodge(width = 0.5), width = 0.5) +

  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.2, size = 0.5) +
  
  scale_fill_manual(values = c("dodgerblue", "red")) +

  ggtitle("Accuracy, Omissions Correct during stage 3") +
  ylab("Proportion") +
  xlab("Session #") +

  theme_classic(base_size = 22)

```

```{r}

pass3 = stage3 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
    ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n()) %>% 
    
    ungroup()

```


```{r}

pass3sum = pass3 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass3sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

# Stage 4 to pass

```{r}

stage4 = train %>%
  
  filter(Stage == 4) %>%
  
  group_by(ID)

head(stage4)

```

How many sessions to graduate? 

```{r}

stage4 %>% 
  
  count(Group, Sex)

```

```{r}

promotion4 = train %>%
  
  filter(Stage == 4) %>%
  
  group_by(ID) %>% 
  
  mutate(Session = match(Date,
                         unique(Date))) %>% 
  
  ungroup() %>% 
  
  group_by(ID, Session) %>%
  
  summarise(.nCor = sum(Response == "Correct") / 100 ,
            
            Corr = sum(Response == "Correct") / max(Trials),
            Accu = sum(Response == "Correct") /
                     (sum(Response == "Correct") + sum(Response == "Incorrect")),
            Omis = sum(Response == "Omission") / max(Trials),
            Prem = sum(Response == "Premature") / max(Trials),
            Pers = sum(Response == "Perseverative") / max(Trials),
            Time = sum(Response == "Timeout") / max(Trials)
            
            ) %>%
  
  pivot_longer(cols = .nCor:Time) %>% 
  
  ungroup()

```


```{r, fig.width=12, fig.height=12}

ggplot(promotion4 %>% 
         
         filter(name == "Accu"|
                  name == "Omis"),

       aes(as.factor(Session),
           value,
           fill = name)

       ) +

  facet_wrap(~ ID,
             ncol = 8) +

  geom_hline(yintercept = 0.8,
             color = "dodgerblue") +
  
  geom_hline(yintercept = 0.5,
             color = "red") +
  
  stat_summary(fun = "mean", geom = "col",
               alpha = 0.5,
               position = position_dodge(width = 0.5), width = 0.5) +

  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.2, size = 0.5) +
  
  scale_fill_manual(values = c("dodgerblue", "red")) +

  ggtitle("Accuracy, Omissions Correct during stage 4") +
  ylab("Proportion") +
  xlab("Session #") +

  theme_classic(base_size = 22)

```

```{r}

pass4 = stage4 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
    ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n()) %>% 
    
    ungroup()

```


```{r}

pass4sum = pass4 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass4sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

# Stage 5 to pass

```{r}

stage5 = train %>%
  
  filter(Stage == 5) %>%
  
  group_by(ID)

head(stage5)

```

How many sessions to graduate? 

```{r}

stage5 %>% 
  
  count(Group, Sex)

```

```{r}

promotion5 = train %>%
  
  filter(Stage == 5) %>%
  
  group_by(ID) %>% 
  
  mutate(Session = match(Date,
                         unique(Date))) %>% 
  
  ungroup() %>% 
  
  group_by(ID, Session) %>%
  
  summarise(.nCor = sum(Response == "Correct") / 100 ,
            
            Corr = sum(Response == "Correct") / max(Trials),
            Accu = sum(Response == "Correct") /
                     (sum(Response == "Correct") + sum(Response == "Incorrect")),
            Omis = sum(Response == "Omission") / max(Trials),
            Prem = sum(Response == "Premature") / max(Trials),
            Pers = sum(Response == "Perseverative") / max(Trials),
            Time = sum(Response == "Timeout") / max(Trials)
            
            ) %>%
  
  pivot_longer(cols = .nCor:Time) %>% 
  
  ungroup()

```


```{r, fig.width=12, fig.height=12}

ggplot(promotion5 %>% 
         
         filter(name == "Accu"|
                  name == "Omis"),

       aes(as.factor(Session),
           value,
           fill = name)

       ) +

  facet_wrap(~ ID,
             ncol = 8) +

  geom_hline(yintercept = 0.8,
             color = "dodgerblue") +
  
  geom_hline(yintercept = 0.5,
             color = "red") +
  
  stat_summary(fun = "mean", geom = "col",
               alpha = 0.5,
               position = position_dodge(width = 0.5), width = 0.5) +

  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.2, size = 0.5) +
  
  scale_fill_manual(values = c("dodgerblue", "red")) +

  ggtitle("Accuracy, Omissions Correct during stage 5") +
  ylab("Proportion") +
  xlab("Session #") +

  theme_classic(base_size = 22)

```

```{r}

pass5 = stage5 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
    ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n()) %>% 
    
    ungroup()

```


```{r}

pass5sum = pass5 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass5sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

# Stage 6 - graduated training

```{r}

stage6 = train %>%
  
  filter(Stage == 6) %>%
  
  group_by(ID)

head(stage5)

```

How many sessions in this stage?

```{r}

stage6 %>% 
  
  count(Group, Sex)

```

```{r}

promotion6 = train %>%
  
  filter(Stage == 6) %>%
  
  group_by(ID) %>% 
  
  mutate(Session = match(Date,
                         unique(Date))) %>% 
  
  ungroup() %>% 
  
  group_by(ID, Session) %>%
  
  summarise(.nCor = sum(Response == "Correct") / 100 ,
            
            Corr = sum(Response == "Correct") / max(Trials),
            Accu = sum(Response == "Correct") /
                     (sum(Response == "Correct") + sum(Response == "Incorrect")),
            Omis = sum(Response == "Omission") / max(Trials),
            Prem = sum(Response == "Premature") / max(Trials),
            Pers = sum(Response == "Perseverative") / max(Trials),
            Time = sum(Response == "Timeout") / max(Trials)
            
            ) %>%
  
  pivot_longer(cols = .nCor:Time) %>% 
  
  ungroup()

```


```{r, fig.width=12, fig.height=12}

ggplot(promotion6 %>% 
         
         filter(name == "Accu"|
                  name == "Omis"),

       aes(as.factor(Session),
           value,
           fill = name)

       ) +

  facet_wrap(~ ID,
             ncol = 8) +

  geom_hline(yintercept = 0.8,
             color = "dodgerblue") +
  
  geom_hline(yintercept = 0.5,
             color = "red") +
  
  stat_summary(fun = "mean", geom = "col",
               alpha = 0.5,
               position = position_dodge(width = 0.5), width = 0.5) +

  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.2, size = 0.5) +
  
  scale_fill_manual(values = c("dodgerblue", "red")) +

  ggtitle("Accuracy, Omissions Correct during stage 6") +
  ylab("Proportion") +
  xlab("Session #") +

  theme_classic(base_size = 22)

```

```{r}

pass6 = stage6 %>% 
  
  group_by(Group, Sex, ID, Date) %>%
  
  arrange(Date) %>% 
  
  summarise(Correct = sum(Response == "Correct")) %>% 
  
    ungroup() %>% 
  
  group_by(Group, Sex, ID) %>%
  
  mutate(Session = 1:n()) %>% 
    
    ungroup()

```


```{r}

pass6sum = pass6 %>% 
  
  group_by(Group, Sex, ID) %>% 
  
  summarise(Days = n())

```


```{r}

ggplot(pass6sum,
       
  aes(Group,
      
      Days,
      
     color = Group,
      
      fill = Group,
      
      label = ID)) +
  
  geom_text_repel() + 
  
  geom_point(position = position_jitter(seed = 1,
                                       
                                       width = 0.1,
                                       
                                       height = 0.1)) +
  
  stat_summary(fun = "mean",
               
               geom = "col",
               
               width = 0.33,
               
               alpha = 0.25) +
  
  stat_summary(fun.data = "mean_se",
               
               geom = "errorbar",
               
               size = 1,
               
               width = 0.1) +
  
  # #scale_color_manual(values = c("blue", "red")) +

  theme_classic(base_size=22)

```

